### 2016-04-30 text/Chapter04.tex
Some more edits (Chapter 5)
Unique structural derivation and edits (Chapter 6)

\setcounter{chapter}{3}
\chapter{Types for flat coeffects}
\label{ch:flat}

@@

\vspace{0.5em}\noindent\hangindent=0.7cm
Cases (\emph{var}), (\emph{const}), (\emph{app}), (\emph{let}), (\emph{param}) and (\emph{letpar})
  similarly to (\emph{abs}).
\end{proof}

@@

\begin{theorem}[Uniqueness of coeffect typing for liveness and dataflow]
\label{thm:flat-ldf-unique}
In the type system for implicit parameters defined in Figure~\ref{fig:flat-types} with the (abs)
rule replaced by (idabs), when $\coctx{\Gamma}{\cclrd{r}} \vdash e : \tau$ and
$\coctx{\Gamma}{\cclrd{r'}} \vdash e : \tau'$ then $\tau = \tau'$ and $\cclrd{r} = \cclrd{r'}$.
\end{theorem}
\begin{proof}
Suppose that (A) $\coctx{\Gamma}{\cclrd{c}} \vdash e : \tau$ and
(B) $\coctx{\Gamma}{\cclrd{c'}} \vdash e : \tau'$. We show by induction over the typing
derivation of $\coctx{\Gamma}{\cclrd{c}} \vdash e : \tau$ that $\tau = \tau'$ and $\cclrd{c}=\cclrd{c'}$.

\vspace{0.5em}\noindent\hangindent=0.6cm
Case (\emph{abs}): $e = \lambda x\!:\!\tau_1.e_1$. $\tau = \tau_1 \xrightarrow{\cclrd{c}} \tau_2$
  for some $\tau_2$ and $\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{c}} \vdash e : \tau_2}$.
  By case (5) of Lemma~\ref{thm:flat-ldf-invert}, the final rule of the derivation (B) must
  have also been (\emph{abs}) and this derivation has a sub-derivation with a conclusion
  ${\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{c'}} \vdash e : \tau_2'}$.
  By the induction hypothesis $\tau_2 = \tau_2'$ and $\cclrd{c}=\cclrd{c'}$ and therefore
  also so $\tau = \tau'$.

\vspace{0.5em}\noindent\hangindent=0.7cm
Cases (\emph{var}), (\emph{const}), (\emph{app}), (\emph{let}), (\emph{param}) and (\emph{letpar})
  similarly to (\emph{abs}).
\end{proof}

>>>>

\chapter{Types for flat coeffects}
\label{ch:flat}

@@

\vspace{0.5em}\noindent\hangindent=0.7cm
Cases (\emph{app}), (\emph{let}) and (\emph{letpar})
  similarly to (\emph{abs}).
\end{proof}

@@

\begin{theorem}[Uniqueness of coeffect typing for liveness and dataflow]
\label{thm:flat-ldf-unique}
In the type system for liveness and dataflow defined in Figure~\ref{fig:flat-types} with the (abs)
rule replaced by (idabs), when $\coctx{\Gamma}{\cclrd{r}} \vdash e : \tau$ and
$\coctx{\Gamma}{\cclrd{r'}} \vdash e : \tau'$ then $\tau = \tau'$ and $\cclrd{r} = \cclrd{r'}$.
\end{theorem}
\begin{proof}
Suppose that (A) $\coctx{\Gamma}{\cclrd{c}} \vdash e : \tau$ and
(B) $\coctx{\Gamma}{\cclrd{c'}} \vdash e : \tau'$. We show by induction over the typing
derivation of $\coctx{\Gamma}{\cclrd{c}} \vdash e : \tau$ that $\tau = \tau'$ and $\cclrd{c}=\cclrd{c'}$.

\vspace{0.5em}\noindent\hangindent=0.6cm
Case (\emph{abs}): $e = \lambda x\!:\!\tau_1.e_1$. Then $\tau = \tau_1 \xrightarrow{\cclrd{c}} \tau_2$
  for some $\tau_2$ and $\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{c}} \vdash e : \tau_2}$.
  By case (5) of Lemma~\ref{thm:flat-ldf-invert}, the final rule of the derivation (B) must
  have also been (\emph{abs}) and this derivation has a sub-derivation with a conclusion
  ${\coctx{\Gamma, x\!:\!\tau_1}{\cclrd{c'}} \vdash e : \tau_2'}$.
  By the induction hypothesis $\tau_2 = \tau_2'$ and $\cclrd{c}=\cclrd{c'}$ and therefore
  also $\tau = \tau'$.

\vspace{0.5em}\noindent\hangindent=0.7cm
Cases (\emph{var}), (\emph{const}) are direct consequence of Lemma~\ref{thm:flat-ldf-invert}.

\vspace{0.5em}\noindent\hangindent=0.7cm
Cases (\emph{app}) and (\emph{let}) similarly to (\emph{abs}).
\end{proof}
